Tweets

### 2020-05-18 Rmd/jse-2019-ms.Rmd
added text about crontab

>>>>

Setting up the query task with `crontab` is straightforward. On our computer, with Ubuntu 20.04 linux operating system, we opened a terminal and typed `crontab -e`. This opened a text file containing user-specified tasks. We added the following line to the bottom of the file:

```{bash}
*/5 * * * * R -e 'rtweet::stream_tweets(timeout = (60 * 5), parse = FALSE, file_name = paste0("~/work/mentoring/mentoring-framework/data/", lubridate::now(), "-tweets"))'
```

Users may need to slightly amend the above line to conform to requirements of their operating system's `crontab`.

### 2020-05-18 Rmd/tweets.Rmd
added text about crontab

```{r}
tweets <- recover_stream(path = "../data/2020-05-10 12:00:01-tweets.json", verbose = TRUE) %>%
  dplyr::mutate(status_id = as.character(status_id))
```

@@

```{r}
broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = format(status_id, scientific = FALSE))
readr::write_csv(tibble::tibble(status_id = c(tweets$status_id, broken_ids$status_id)), col_names = FALSE, path = "../data/2020-05-10-status-ids.csv")
```

## Rehydrate tweets by querying Twitter

```{r}
# need multiple calls to get all tweets rehydrated
tweets_rehydrated <- rtweet::lookup_tweets(statuses = tweets$status_id, parse = TRUE)
```

>>>>

```{r}
tweets <- recover_stream(path = "../data/2020-05-10 12:00:01-tweets.json", verbose = TRUE) 
tweets %>%
  dplyr::select(status_id) %>%
  readr::write_csv(path = "../data/tweets-status-ids-2020-05-10.csv", col_names = FALSE)
```

@@

```{r}
broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
```

## Hydrate tweets by querying Twitter

```{r}
ids <- readr::read_csv("../data/tweets-status-ids-2020-05-10.csv", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = as.character(status_id))
# need multiple calls to get all tweets rehydrated
tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                            parse = TRUE)
tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
tweets_rehydrated <- tweets_rehydrated1 %>%
  dplyr::bind_rows(tweets_rehydrated2)
```
